%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Pritam Dalal}{}

\address{2340 River Pointe Circle - Minneapolis, MN 55411}

\mobile{612.400.4733}
\email{\href{mailto:pritamdalal@hotmail.com}{\nolinkurl{pritamdalal@hotmail.com}}}
\github{pritamdalal}
\linkedin{pritamdalal}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------


\geometry{left=2.0cm, top=2.0cm, right=2.0cm, bottom=2.0cm, footskip=0.0cm}

% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{summary}{%
\section{Summary}\label{summary}}

\begin{itemize}
\item
  Quantitative professional with 12 years of experience in research,
  data science, and trading roles.
\item
  University of Minnesota adjunct faculty teaching graduate students
  machine learning and data science through appointments in the School
  of Mathematics and the Carlson School of Business.
\item
  Master's in Financial Mathematics (University of Minnesota) and
  Bachelor's in Mathematics and Economics (University of California,
  Berkeley).
\item
  Experienced in data science, machine learning, and statistics: random
  forest, gradient boosted trees, GARCH, neural networks, principal
  component analysis, regression.
\item
  Development experience in Python, R, MySQL, PostgreSQL, Excel, and
  VBA.
\item
  Financial services experience working with options, commodities,
  futures, variance swaps, interest rate swaps, mortgages, corporate
  debt, asset-backed securities, annuities.
\end{itemize}

\hypertarget{experience}{%
\section{Experience}\label{experience}}

\textbf{Posit (RStudio) - Minneapolis, MN} \hfill 2021 - Present

\vspace{-1ex}

Customer Success Manager

\vspace{-1.5ex}

\small

\begin{itemize}
\item
  Work with Posit's largest financial services clients to ensure
  successful adoption of Posit's professional products; the primary
  sales success metric is renewal rate (gross dollar retention).
  \vspace{-0.5ex}
\item
  For 2021, achieved a gross dollar retention of 93\% versus a quota of
  89\%. For 2022, achieved 91.5\% versus a quota of 89\%.
  \vspace{-0.5ex}
\item
  Conduct a variety of client-facing webinars and seminars on Python, R,
  and Posit professional products. \vspace{-0.5ex}
\item
  Lead a series of internal trainings on data wrangling in Python.
  \vspace{-0.5ex}
\end{itemize}

\normalsize

\textbf{University of Minnesota - Minneapolis, MN} \hfill 2018 - Present

\vspace{-1ex}

Adjunct Faculty

\vspace{-1.5ex}

\small

\begin{itemize}
\item
  Develop and teach machine learning and data analysis courses using
  Python and R courses for the Master of Financial Mathematics program;
  tutorials developed in Jupyter Notebooks and R Markdown notebooks,
  slide presentations written in R Markdown. \vspace{-0.5ex}
\item
  Faculty mentor for final project of Carlson School of Business Master
  of Science in Finance program. \vspace{-0.5ex}
\item
  Developed an R package to clean and wrangle a large database of
  historical options data; implemented an on-premise Postgres database
  for data storage. \vspace{-1.75ex}
\end{itemize}

\begin{itemize}
\item
  Machine Learning:
  \href{https://github.com/pritamdalal/python\_for\_machine\_learning\_in\_finance}{https://github.com/pritamdalal/python\_for\_machine\_learning\_in\_finance}
  \vspace{-0.5ex}
\item
  Python:
  \href{https://github.com/pritamdalal/python\_for\_data\_wrangling\_in\_finance}{https://github.com/pritamdalal/python\_for\_data\_wrangling\_in\_finance}
  \vspace{-0.5ex}
\item
  R:
  \href{https://pritamdalal.github.io/rff\_course/}{https://pritamdalal.github.io/rff\_course/}
  \vspace{-0.5ex}
\end{itemize}

\normalsize

\textbf{Aware Asset Management - St Paul, MN} \hfill 2019 - 2021

\vspace{-1ex}

Head of Quantitative Research

\vspace{-1.5ex}

\small

\begin{itemize}
\item
  Determined the quantitative research agenda for all of Aware's
  investment strategies spanning corporate debt, mortgage backed
  securities, and asset backed securities. \vspace{-0.5ex}
\item
  Developed machine learning models for predicting student loan defaults
  in JupyterLab with Python's scikit-learn package; features were
  selected from Intex CDU files, and a variety of classification models
  were employed including logistic regression, decision tree, and random
  forest. \vspace{-2ex}
\end{itemize}

\begin{itemize}
\tightlist
\item
  Contributed to marketing through media interviews, podcast
  appearances, and monthly newsletter authorship. \vspace{-0.5ex}
\end{itemize}

\normalsize

\vspace{100ex}

\textbf{Incenter - St.~Paul, MN} \hfill 2016 - 2017

\vspace{-1ex}

Trader Analyst

\vspace{-1.5ex}

\small

\begin{itemize}
\item
  Priced and calculated sensitivities for MSR, reverse mortgages, and
  other mortgage products; data warehouses were located in Azure and
  computations were executed in R and VBA. \vspace{-0.5ex}
\item
  Developed and implemented the TBA and interest rate swap hedging
  strategies; developed custom R functions for valuing interest rate
  swaps. \vspace{-0.5ex}
\item
  Trade execution for hedge rebalances on TBA positions and interest
  rate swap positions. \vspace{-0.5ex}
\end{itemize}

\normalsize

\textbf{Wolverine Trading - Chicago, IL} \hfill 2015 - 2016

\vspace{-1ex}

Data Scientist

\vspace{-1.5ex}

\small

\begin{itemize}
\tightlist
\item
  Performed reporting, data analysis, and predictive analytics on
  various aspects of automated market-making systems utilizing R, SQL,
  Tableau, and Tableau Server; data sources included OPRA, exchange
  reporting, and proprietary data generated from the market-making
  strategies. \vspace{-2ex}
\end{itemize}

\begin{itemize}
\item
  Lead the analytics development for Wolverine's liquidity taking
  strategies; created a visualization-based dashboard in Tableau to
  stratify fill-rate statistics. \vspace{-0.5ex}
\item
  Played a key role in the transition to Tableau for reporting and
  analysis. \vspace{-0.5ex}
\end{itemize}

\normalsize

\textbf{Two Harbors Investment Corp - Minneapolis, MN } \hfill 2014 -
2015

\vspace{-1ex}

MSR Servicer Performance Consultant (Contract)

\vspace{-1.5ex}

\small

\begin{itemize}
\item
  Analyzed loan-level and repline-level data to develop various
  portfolio performance analytics for the purposes of MSR subservicer
  oversight, using C\#, VBA, and Excel; data warehouses located in
  on-premise Microsoft SQL Server databases. \vspace{-0.5ex}
\item
  Analyzed cash-flows and remittances to validate subservicer billing
  statements to determine if foreclosure processes were properly billed.
  \vspace{-0.5ex}
\item
  Researched historical delinquency rates in Ginnie Mae collateral by
  analyzing various data sources provided by the Government Sponsored
  Entities. \vspace{-0.5ex}
\end{itemize}

\normalsize

\textbf{Hedge Fund Launch Development - Minneapolis, MN } \hfill 2012 -
2014

\vspace{-1ex}

Principal and Researcher

\vspace{-1.5ex}

\small

\begin{itemize}
\item
  Backtested various volatility trading strategies on equities and ETFs,
  using R, Excel, and VBA; this involved empirical research in portfolio
  optimization and variance forecasting. \vspace{-0.5ex}
\item
  Built an on-premise MySQL research database for historical end-of-day
  option prices, intraday option prices, parametric fitted skews, equity
  corporate actions, and variance estimates. \vspace{-0.5ex}
\item
  Developed a working knowledge of the Interactive Brokers C\# API, and
  used the API for intraday data capture of option prices and order book
  depth. \vspace{-0.5ex}
\item
  Explored legal and regulatory issues involving the hedge fund
  industry.
\end{itemize}

\normalsize

\textbf{Cargill - Minneapolis, MN} \hfill 2008 - 2012

\vspace{-1ex}

Junior Trader

\vspace{-1.5ex}

\small

\begin{itemize}
\tightlist
\item
  Developed, backtested, and implemented a proprietary commodity
  volatility trading strategy; this research was conducted in VBA and
  Excel, with an Oracle database backend. \vspace{-2ex}
\end{itemize}

\begin{itemize}
\item
  Managed and hedged portfolios of exotic derivatives on various
  commodity futures. \vspace{-0.5ex}
\item
  Data analysis of skew-based models for pricing and replicating digital
  and barrier options using R. \vspace{-0.5ex}
\item
  Developed and implemented an interest rate hedging strategy using
  Eurodollar futures. \vspace{-0.5ex}
\item
  Extensive experience trading exchange and OTC options on commodity
  futures. \vspace{-0.5ex}
\item
  Created and presented finance training seminars for non-traders.
  \vspace{-0.5ex}
\end{itemize}

\pagebreak

\normalsize

\textbf{Allianz Investment Management - Minneapolis, MN} \hfill 2007 -
2008

\vspace{-1ex}

Quantitative Analyst

\vspace{-1.5ex}

\small

\begin{itemize}
\item
  Structured, priced, and hedged fixed and variable annuity benefits.
  \vspace{-0.5ex}
\item
  Systems development for the hedging platform including risk analytics,
  sensitivity analysis; primary technologies were VBA and Excel.
  \vspace{-0.5ex}
\item
  Research and backtesting projects on topics such as model selection,
  Monte-Carlo methods, and option replication. \vspace{-0.5ex}
\end{itemize}

\normalsize

\hypertarget{education}{%
\section{Education}\label{education}}

\textbf{University of Minnesota, Twin Cities}

\vspace{-1ex}

Master of Financial Mathematics

\vspace{-1ex}

GPA: 4.0

\textbf{University of California, Berkeley}

\vspace{-1ex}

Bachelors of Arts, Mathematics and Economics (honors)

\vspace{-1ex}

GPA: 3.42

\hypertarget{technical-expertise}{%
\section{Technical Expertise}\label{technical-expertise}}

\textbf{Computing Technology}

\vspace{-1ex}

Python, R, SQL, Tableau, Excel, VBA

\textbf{Communication Tools}

\vspace{-1ex}

Jupyter Notebook, Quarto, R Markdown, \LaTeX

\textbf{Machine Learning, Statistics, and Mathematics}

\vspace{-1ex}

Random Forest, Regression, Logistic Regression, Decision Trees, GARCH,
Principal Components Analysis, Neural Networks, Linear Algebra, Real
Analysis, Probability

\textbf{Quantitative Finance}

\vspace{-1ex}

Option Replication, Dynamic Hedging, Futures, Commodities, Variance
Swaps, Variance Estimation, Volatility Trading, Interest Rate Swaps,
Mortgage Backed Securities, Mortgage Servicing Rights, Student Loan
Asset Backed Securities, Corporate Bonds



\end{document}
